\documentclass[a4paper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=1.5cm]{geometry}
\usepackage{lmodern}
\renewcommand{\familydefault}{\sfdefault}
\usepackage[dvipsnames]{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}
\input{glyphtounicode}
\pdfgentounicode=1

\definecolor{accent}{HTML}{0D9488}
\definecolor{muted}{HTML}{444B53}

\setlength{\parindent}{0pt}
\pagestyle{empty}
\hypersetup{urlcolor=accent}

\newenvironment{tight}
  {\begin{list}{\textcolor{accent}{\small$\bullet$}}{%
      \setlength{\leftmargin}{1.4em}%
      \setlength{\itemsep}{1.5pt}%
      \setlength{\topsep}{2pt}%
      \setlength{\parsep}{0pt}}}
  {\end{list}}

\newcommand{\cvsection}[1]{%
  \vspace{9pt}%
  {\color{accent}\large\bfseries\MakeUppercase{#1}}\par\vspace{2pt}%
  {\color{accent}\hrule height 1.1pt}\vspace{5pt}%
}

\newcommand{\entry}[2]{\textbf{#1}\hfill{\color{muted}#2}\par}
\newcommand{\subentry}[2]{{\itshape #1}\hfill{\color{muted}\itshape #2}\par\vspace{2pt}}

\begin{document}

\begin{center}
  {\Huge\bfseries Mert \textcolor{accent}{Çelik}}\par\vspace{4pt}
  {\color{muted}Software Engineering Student \textbar\ Working Student}\par\vspace{4pt}
  \small Berlin, Germany \quad\textbar\quad
  \href{mailto:sw3doo@gmail.com}{sw3doo@gmail.com} \quad\textbar\quad
  \href{https://github.com/sw3do}{github.com/sw3do} \quad\textbar\quad
  \href{https://sw3do.github.io}{sw3do.github.io} \quad\textbar\quad
  \href{https://linkedin.com/in/swedo}{linkedin.com/in/swedo}
\end{center}

\vspace{6pt}
\small Software Engineering B.Sc. student in Berlin who builds backends, command-line tools and full-stack apps in Rust, Go and TypeScript. Looking for a working-student (Werkstudent) role, up to 20 hours per week.

\cvsection{Technical Skills}
\small
\textbf{Languages:} Rust, Go, Python, TypeScript / JavaScript, Java, Dart \par
\textbf{Backend:} Axum, SQLx, NestJS, Node.js, REST APIs, PostgreSQL, MySQL \par
\textbf{Frontend:} Next.js, React, Svelte, Vue, Astro, Tailwind CSS \par
\textbf{Systems \& Tooling:} Linux, Docker, Git, Tauri, FFmpeg, serial-port / hardware integration \par
\textbf{Machine Learning:} TensorFlow, Keras \par

\cvsection{Projects}
\small
\entry{jikan-rs}{\href{https://github.com/sw3do/jikan-rs}{github.com/sw3do/jikan-rs}}
{\color{muted}\itshape Rust async library, published to crates.io}\par
\begin{tight}
  \item Wrote and published an async Rust client for the Jikan (MyAnimeList) API, covering every v4 endpoint, with typed \texttt{serde} models and built-in rate limiting (3 req/s, burst of 5).
\end{tight}
\vspace{3pt}
\entry{packet-sniffer}{\href{https://github.com/sw3do/packet-sniffer}{github.com/sw3do/packet-sniffer}}
{\color{muted}\itshape Go, libpcap, BPF}\par
\begin{tight}
  \item Built a cross-platform network analyzer in Go that captures traffic in real time, reads TCP/UDP/ICMP/HTTP/DNS, filters with BPF, and flags suspicious activity.
\end{tight}
\vspace{3pt}
\entry{nsfw-detector}{\href{https://github.com/sw3do/nsfw-detector}{github.com/sw3do/nsfw-detector}}
{\color{muted}\itshape Python, TensorFlow / Keras}\par
\begin{tight}
  \item Built an image classifier that checks for NSFW content, served as a Python library and a small REST API.
\end{tight}
\vspace{3pt}
\entry{discord-custom-rpc}{\href{https://github.com/sw3do/discord-custom-rpc}{github.com/sw3do/discord-custom-rpc}}
{\color{muted}\itshape Tauri, Vue 3, Rust}\par
\begin{tight}
  \item Built a cross-platform desktop app (Rust core, Vue 3 UI) for creating and managing custom Discord Rich Presence.
\end{tight}

\cvsection{Education}
\small
\entry{GISMA University of Applied Sciences}{Berlin, Germany}
\subentry{B.Sc. Software Engineering}{Currently enrolled}

\cvsection{Experience}
\small
\entry{Working Student, Software \& Operations}{Berlin, Germany}
\subentry{Bar \& Entertainment Venue}{Part-time}
\begin{tight}
  \item Built small internal tools and automated some repetitive tasks on Linux.
  \item Wrote serial-port code so our software could talk to the physical machines while they were running.
\end{tight}

\cvsection{Languages}
\small
Turkish --- Native (C2) \quad\textbar\quad English --- Professional working proficiency (C1) \quad\textbar\quad German --- Basic, actively improving (A1)

\end{document}
